First estimate of a galaxy rotational velocity from its observed Lyman-$\alpha$ line

### 2015-04-25 paper/ms.tex

Theoretical background...\\

>>>>

\cite{Garavito14} presented an analytical expresion that approximates
the results for the Lyman-$\alpha$ line morphology for a spherical galaxy
rotating as a solid body.

Ths input parameters of the analytical solution are the optical depth
$\tau_{H}$, the rotational velocity at the sphere's surface $V_{\rm
  max}$ and the angle of view measured from the equatorial plane
(which is perpendicular to the rotational axis) $\theta$. 
A $\texttt{C}$ source code implementation is available in the public
repository associated to this paper.

The main result \cite{Garavito14} is that rotation does have a
noticeable impact on the \ly line morphology.
This impact is two fold. 
First, the rotation axis breaks the spherical symmetry, introducing a
dependence of the line shape with viewing angle.
Second, for increasing rotational velocities and viewing angles off
the rotational axis, the intensity at the line's centers increases;
for sufficiently high rotational velocities the line becomes single peaked.
